\documentclass[12pt]{article}
\usepackage{fullpage}
\special{papersize=8.5in,11in}
\usepackage[LabelsAligned]{currvita}
\usepackage{color}
\pagecolor{white}
\newcommand*{\ac}[1]{\mbox{#1}}
\tolerance=600
\begin{document}
\setlength{\cvlabelsep}{2mm}
\setlength{\cvlabelwidth}{13mm}
\begin{cv}{} 
\begin{center}
  \textbf{
  SERGIO J. REY Jr.}\\
\textsc{Curriculum Vitae} 
\vspace{.25in}
\end{center}
\begin{center}
  \begin{tabular}{ll}
    \textbf{Mailing Address}&\textbf{Contact Information}\\
    School of Geographical Sciences and Urban Planning&Tel: (408) 965-7433\\
    Arizona State University&Fax: (408) 965-8313\\
    PO Box 875302&Email: srey@asu.edu\\
    Tempe, AZ 85287-5302&Web: http://geoplan.asu.edu/rey\\
   \end{tabular}
\end{center}

 \begin{cvlist}{Education}
\item[1994] Ph.D. Geography, University of California, Santa
   Barbara. 
\item[1988] M.A. Geography, University of California, Santa Barbara.
\item[1985] B.S. Environmental Science, The Richard Stockton College of New Jersey.
  \end{cvlist}

  \begin{cvlist}{Academic Appointments}
\item[Professor,] School of Geographical Sciences and Urban Planning, Arizona
  State University
\item[Faculty Research Affiliate,] Regional Research Institute, West Virginia
  University
\item[Affiliate Research Professor,] Regional Economics Applications
  Laboratory, The University of Illinois at Urbana-Champaign
\item[Adjunct Professor,] Department of Geography, San Diego State
  University
\end{cvlist}
\begin{cvlist}{Prior Academic Appointments}
\item[2007-08] Chair, Department of Geography, San Diego State
\item[2006-08] Co-director, Center For Earth Systems Analysis Research (CESAR),
  Department of Geography, San Diego State University
 \item[2005-08] Director, Regional Analysis Laboratory (REGAL), Department of
   Geography, San Diego State University
 \item[2005-08] Adjunct Faculty Member, Department of Geography, University of
   Illinois, Champaign-Urbana
 \item[2003-08] Professor, Department of Geography, San Diego State
 University
 \item[2001] Visiting Scholar, School of Economics, University of
  Queensland (Summer-Fall).
 \item[1998--03] Associate Professor, Department of Geography, San Diego State University
 \item[1994--08] SDSU/UCSB Geography Ph.D. Faculty member. 
 \item[1994--98] Assistant Professor, Department of Geography, San Diego State University
  \end{cvlist}

  \begin{cvlist}{Editorial Appointments}
  \item[2013--] Editorial board member, \emph{Geographical Analysis}
  \item[2011--] Editorial board member, \emph{Spatial Demography}
  \item[2008--] Editorial board member, \emph{Computers, Environment and Urban Systems}
  \item[2008--] Editorial board member, \emph{R\'egion et D\'eveloppement}
 \item[2007--] Editorial board member, \emph{Letters in Spatial and Resource
	 Sciences}
 \item[1999--] Editor, \emph{International Regional Science Review}
  \item[1999-10] Editorial board member, \emph{Papers in Regional
  Science}
  \item[1998] Book review editor, \emph{The Professional
  Geographer} \item[1997-99] Editorial board member, \emph{International
  Regional Science Review}
 \item[1996--08] Editorial board member, \emph{Geographical Analysis}
\item[\textbf{{Themed Issues}}]
\item[2011] Co-editor, ``Special Issue in Honor of Manfred Fischer.''
  \emph{International Regional Science Review}.
\item[2006] Guest Co-editor, ``The Spatial Dimensions of Economic Growth and
    Convergence.'' \emph{Papers in Regional Science}.
\item[2006] Guest Co-editor, ``Recent Advances in Software for Spatial Analysis in
  the Social Sciences.'' \emph{Geographical Analysis}.
\item[2004] Guest editor, ``Special Issue on Walter Isard's Impact on
  Analytical Human Geographic Research.'' \emph{Journal of Geographic
  Systems}.
 \item[2001] Co-editor, ''Special Issue in Honor of William Alonso.``
   \emph{International Regional Science Review}.
  \item[1997] Guest Co-editor, ``Special Issue
  on Spatial Econometrics'' \emph{International Regional Science Review}
  \end{cvlist}
 
\begin{cvlist}{Honors and Awards}
\item[2014] President, Western Regional Science Association
 \item[2007-] Fellow, Spatial Econometrics Association
 \item[1999-00] Faculty Fellow. Center on Computational Science and
  Engineering. San Diego State University.
 \item[1998] Geoffrey J.D. Hewings Distinguished Young Scholars
  Award. North American Regional Science Council.
\end{cvlist}
\pagebreak
  \begin{cvlist}{Publications}
 \item[\textbf{Books and Edited Volumes}]

\item[2010] Anselin, L. and S.J. Rey (eds.) \emph{Perspectives on Spatial Data
  Analysis}. Springer Verlag, Berlin. 
\item[2004] Anselin, L., R.J.G.M. Florax and S.J. Rey (eds.),
	\emph{Advances in Spatial Econometrics. Methodology, Tools and
	Applications}. Springer Verlag, Berlin.
\item[2002] Anselin, L. and S.J. Rey (eds.), \emph{New Tools for Spatial Data
	Analysis: Proceedings of a Workshop.} Center for Spatially Integrated
	Social Science, University of California, Santa Barbara (CD-ROM).

 \item[\textbf{Refereed Journal Articles and Book Chapters}]
\item[2014] Mack, E.A.  and S.J. Rey. ``Regional variations in broadband
  linkages with knowledge intensive firms." \emph{Telecommunications
  Policy}, 38(1): 105-118.
\item[2014] Rey, S.J. ``Fast algorithms for a space-time concordance
  measure.'' \emph{Computational Statistics}. Forthcoming.
\item[2014] Rey, S.J. ``Rank based Markov chains for regional income
  distribution dynamics.'' \emph{Journal of Geographical Systems}. DOI:10.1007/s10109-013-0189-0.
\item[2014] Rey, S.J., A.T. Murray, T.H. Grubesic, E. Mack, R. Wei, L. Anselin
  and M. Griffin. ``Sex Offender Residential Movement Patterns: A Markov Chain
  Analysis.'' \emph{Professional Geographer}, 66(1): 102-111.
\item[2013] Anselin, L., A.T. Murray and S.J. Rey. ``Spatial Analysis.'' In T.
  Little (ed.) \emph{Oxford Handbook of Quantitative Methods}. Oxford
  University Press. Pages 154-174.
\item[2013] Franklin, J., G. Keppel, E. Webb, J. Seamon, S. Rey, D. Steadman,
  D. Drake and S. Wiser. ``Dispersal limitation, speciation, environmental
  filtering and niche differentiation influence forest tree communities in
  West Polynesia.'' \emph{Journal of Biogeography}, 40: 988-99. 
\item[2013] Laura, J. and S.J. Rey. ``Improved parallel optimum choropleth map
  classification.'' In Shi, X., V. Kindratenko and C. Yang (eds.) \emph{Modern Accelerator Technologies
  (MAT) for Geographic Information Science}. Springer: Berlin. Pages
  197-212.
\item[2013] Mack, E.A., Y. Zheng, S.J. Rey and R. Maciejewski.
  ``Spatio-temporal analysis of industrial composition with IVIID: An
  Interactive Visual Analytics Interface for Industrial Diversity.''
  \emph{Journal of Geographical Systems}. Accepted 2013-09-06.
\item[2013] Rey, S.J. ``Regional income distribution dynamics revisited.''
  \emph{Regional and Urban Economics.} Accepted 2013-09-04.
\item[2013] Rey, S.J., L. Anselin, R. Pahle, X. Kang, and P. Stephens.
  ``Parallel Optimal Choropleth Map Classification in PySAL.''
  \emph{International Journal of Geographical Information Science},
  27(5): 1023-1039
\item[2013] Rey, S.J.  and R. Smith. ``A spatial decomposition of the Gini
  coefficient.'' \emph{Letters in Spatial and Resources Sciences.}, 6(2):
  52-70.
\item[2013] Sastr\'e-Guti\'errez, M.L. and S.J. Rey. ``Space-time income
  distribution dynamics in Mexico.'' \emph{Annals of GIS}, 19(3):
  195-207.
\item[2012] Anselin, L. and S.J. Rey. ``Spatial econometrics in an age of
  CyberGIS.'' \emph{International Journal of Geographical Information
  Science}. 26(12): 2211-2226.
\item[2012] Kang, X. and S.J. Rey. ``Parallelizing Max-P-Regions Spatial
  Clustering Method in PySAL.'' \emph{Proceedings International Workshop on Modern Accelerator
  Technologies for GIScience}. Columbus.
\item[2012] Mack, E., Malizia, N. and S.J. Rey. ``Population shift-bias in
  tests of space-time interaction.'' \emph{Computers, Environment and Urban
  Systems}, 36(6): 500-512.
\item[2012] Murray, A.T., P. Gober, L. Anselin, S.J. Rey, D.A. Sampson, P.D.
  Padegimas and Y. Liu. ``Spatial optimization models for water supply
  allocation.'' \emph{Water Resources Management}, 26(8): 2243-57. 
\item[2012] Murray, A.T., Grubesic, T.H., Elizabeth A., Wei, M.R., Rey, S.J,
  Anselin, L. and M.L. Griffin: Convicted Sex Offender Residential Movements.
  In M. Leitner (ed.) \emph{Crime Modeling and Mapping using Geospatial
  Technologies.} Springer. Forthcoming.
\item[2012] Rey, S.J. ``Spatial dynamics and space-time data analysis.'' In
  M. Fischer and P. Nijkamp (editors). \emph{Handbook of Regional Science}.
  Springer. Forthcoming. 
\item[2012] Rey, S.J. ``Open source spatial analysis: lessons for research and
  education from PySAL. \emph{Proceedings of the Open Source Geospatial
  Research and Education Symposium}, pages 64-68.
\item[2012] Rey, S.J., E.A. Mack and J. Koschinsky. ``Exploratory space-time
  analysis of burglary patterns.'' \emph{Journal of Quantitative Criminology},
  28(3): 509-531.
\item[2012] Sastr\'e-Guti\'errez, Myrna L. y S.J. Rey.  ``Movilidad
  Espacial del Ingreso en México, en Análisis Espacial y Regional.''
  Crecimiento, Concentración Económica, Desarrollo y Espacio. Serie Análisis
  Regional. Coordinadores: Mendoza M.A., Quintana, L., Asuad, N. Plaza y
  Valdes, Editores. ISBN: 978-607-402-497-5, 91-117.
\item[2011] Duque, J.C., L. Anselin and S.J. Rey. ``The max p-region problem.''
 \emph{Journal of Regional Science} DOI: 10.1111/j.1467-9787.2011.00743.x.
\item[2011] Elias, M. and S.J. Rey. ``Educational convergence in Peru.'' 
\emph{R\'egion et D\'eveloppement}, 33: 107-134. 
\item[2011] Murray, A.T, J. Koschinsky, Y. Liu, S.J. Rey and L. Brown. ``Are
  foreclosures contagious? An exploratory space-time analysis of Ohio's
  Franklin County, 2001-2008.'' \emph{International Journal of Applied
  Geospatial Research}. Forthcoming. 
\item[2011] Murray, A.T, Y. Liu, S.J. Rey and L. Anselin. ``Exploring movement
  object patterns.'' \emph{The Annals of Regional Science}. DOI: 10.1007/s00168-011-0459-z.
\item[2011] Rey, S.J., L. Anselin, D. Folch, D. Arribas, M.L. Sastr\'e Guti\'errez
  and L. Interlante. ``Measuring spatial dynamics in metropolitan areas''.
  \emph{Economic Development Quarterly} 25, 54-64.
\item[2011] Rey, S.J. and D.C. Folch ``Impact of spatial effects on income
  segregation indices.'' \emph{Computers, Environment and Urban Systems}, 35:
  431-441.
\item[2011] Rey, S.J., A.T. Murray, and L. Anselin. ``Visualizing regional
  distribution dynamics.'' \emph{Letters in Spatial and Resource Sciences},
4: 81-90.
\item[2011] Schmidt, C.R., S.J. Rey and A. Skupin. ``Effects of irregular topology
  on self-organizing maps.'' \emph{International Regional Science Review}, 34:
  215-229.
\item[2011] Ye, X. and S.J. Rey. ``A framework for exploratory space-time
  analysis of economic data.'' \emph{The Annals of Regional Science}.
  DOI: 10.1007/s00168-011-0470-4.
\item[2010] Anselin, L. and S.J. Rey. ``Perspectives on spatial data
  analysis.'' In Anselin, L. and S.J. Rey (eds). \emph{Perspectives on Spatial Data
  Analysis}. Springer Verlag, Berlin, pages 1-20.
\item[2010] Anselin, L., S.J. Rey and J. Koschinsky. ``Flexible geospatial
  visual analytics and simulation technologies to enhance criminal justice
  decision support systems.'' \emph{Crime Mapping, A Journal of Research and
  Practice}, 2: 10-31.
\item[2010] Duque, J.C., Rey, S.J and D.A. G\'omez. Identifying industry
  clusters in Colombia based on graph theory. \emph{Ensayos Sobre Po\'itica
  Econ\'omica} 27(59):14-45.
\item[2010] Fitch, D.T., D. Stow, A. Hope and S.J. Rey. ``MODIS vegetation metrics as
	indicators of hydrological response in watersheds of California
	Mediterranean-Type climate zones.'' \emph{Remote Sensing of the
	Environment}. 114: 2513-2523.
\item[2010] Rey, S.J. and L. Anselin. ``PySAL a Python library for spatial analytical
	methods.'' In M.M. Fischer and A. Getis (eds.) \emph{Handbook of
	Applied Spatial Analysis.} Springer Verlag, Berlin, pages 175-193.
\item[2010] Rey, S.J. and M.V. Janikas. ``STARS: Space-Time Analysis of Regional
	Systems.'' In M.M. Fischer and A. Getis (eds.) \emph{Handbook of
	Applied Spatial Analysis.} Springer Verlag, Berlin, pages 91-112.
\item[2010] Rey, S.J. and M.L. Sastr\'e Guti\'errez. ``Interregional inequality
  dynamics in Mexico.'' \emph{Spatial Economic Analysis}, 5, 277-298. 
\item[2010] Rey, S.J. and X. Ye ``Comparative Spatial Dynamics of Regional
  Systems ''. In A. P\'aez, J. Le Gallo, R.Buliung and S. Dall'Erba (eds.)
  \emph{Progress in Spatial Analysis: Theory and Computation, and Thematic
  Applications.} Springer Verlag, Berlin, pages 441-464.
\item[2009] Rey, S.J. ``Show me the code: Open source and spatial analysis.''
  \emph{Journal of Geographical Systems}, 11, 191-207.
\item[2009] Rey, S.J., L. Anselin and M. Hwang ``Manipulation of spatial
  weights using web services.'' \emph{Proceedings of the 17th ACM SIGSPATIAL
  International Conference on Advances in Geographic Information Systems},
  pages 72-80. 
\item[2009] Rey, S.J. and J. Le Gallo ``Spatial analysis of economic
  convergence.'' In T.C. Mills and K. Patterson (eds.) \emph{Palgrave Handbook
  of Econometrics Volume II: Applied Econometrics.} Palgrave Macmillan, New York, pages
  1251-1290.
\item[2008] Gutie\'rrez, M.L. and S.J. Rey ``Polarizaci\'on espacial y din\'amicas
  de la desigualdad interregional en M\'exico.'' Problemas del Desarrollo.
  38: 181-202.
\item[2008] Duque, J.C. and S.J. Rey ``Network based approaches towards industrial
  clustering.'' In G. Maier and U. Blien (eds.) \emph{The economics of
  regional clusters: Networks technology and policy}. Edward Elgar, p 41-68.
\item[2008] Janikas, M.V. and S.J. Rey ``On the Relationships Between Spatial Clustering, Inequality, and
  Economic Growth in the United States: 1969-2000.''\emph{R\'egion et
  D\'eveloppement}, 27: 13-34. 
\item[2007] Guti\'errez, M. and S. J. Rey ``Spatial income mobility in
  Mexico.'' \emph{Revista Latinoamericana de Economía}. 
\item[2007] Rey, S.J. and L. Anselin ``PySAL a Python library for spatial analytical
	methods.'' \emph{The Review of Regional Studies}, 37: 5-27. 
\item[2007] Tague, C., M. Farrell, G. Grant, S. Lewis and S.J. Rey ``Hydrogeologic
  controls on summer stream temperatures in the McKenzie River Basin,
  Oregon.'' \emph{Hydrological Processes}, 21: 3228-3300.
\item[2007]  Franklin, J. and S.J. Rey ``Spatial patterns of regeneration in
  secondary and late-successional tropical forest suggest recruitment
  limitations.''  \emph{Journal of Tropical Ecology}, 23: 1-12.
\item[2006] Bode, E. and S.J. Rey ``The spatial dimenstions of economic
  growth and convergence''. \emph{Papers in Regional Science}, 85: 171-176.
\item[2006] Rey, S.J. and B. Dev ``Sigma convergence in the presence of
  spatial effects.'' \emph{Papers in Regional Science}, 85: 217-234.
\item[2006] Rey, S.J.  ``Integrated regional econometric+input-output
	modeling: Issues and opportunities."  In A. Reggiani, K. Button and P.
	Nijkamp (eds.) \emph{Planning Models}. Edward Elgar.  (Reprint of Rey
	2000). 
\item[2006] Rey, S.J. and L. Anselin ``Recent Advances in Software for Spatial Analysis in the 
  Social Sciences.'' \emph{Geographical Analysis.} 38: 1-4.
\item[2006] Rey, S.J. and M.V. Janikas ``STARS: Space-Time Analysis of Regional
	Systems.'' \emph{Geographical Analysis.} 38: 67-86.
\item[2006] Rey, S.J. ``STARS: Space-Time Analysis of Regional Systems.''
  University of Redlands/Environmental Systems Research Incorporated
  Colloquium CD Series. ESRI. Redlands.
\item[2005] Florax, R.J.G.M, H. Folmer and S.J. Rey ``A Comment on
  Specification Searches in Spatial Econometrics: The Relevance of Hendry's
  Methodology'' \emph{Regional Science and Urban Economics.} 36: 300-308.
 \item[2005] Janikas, M.V. and S.J. Rey ``Spatial clustering, inequality and
   income convergence.'' \emph{R\'egion et D\'eveloppement.} 25: 41-64.
\item[2005] Rey, S.J. and M.V. Janikas ``Regional convergence, inequality and space.''
	  \emph{Journal of Economic Geography}. 5: 155-176.
\item[2004] Rey, S.J., G. West and M.V. Janikas. ``Uncertainty in integrated
	regional models.'' \emph{Economic Systems Research}. 16: 259-277. 
\item[2004] Rey, S.J. ``Walter Isard's impact on analytical human geographic
	research.'' \emph{Journal of Geographical Systems}. 6: 3-6.
\item[2004] Rey, S.J. and M.G. Boarnet. ``A taxonomy of spatial econometric
	models for simultaneous equations systems." In L.  Anselin, R.J.G.M.
	Florax and S.J. Rey (eds.) \emph{Advances in Spatial Econometrics.
	Methodology, Tools and Applications}. Springer Verlag, Berlin.
	Pages 99-119.
\item[2004] Anselin, L., R.J.G.M. Florax and S.J. Rey. ``Econometrics for
	spatial models: Recent advances.'' In  L.  Anselin, R.J.G.M. Florax
	and S.J. Rey (eds.) \emph{Advances in Spatial Econometrics.
	Methodology, Tools and Applications}. Springer Verlag, Berlin.
	Pages 1-25.
\item[2004] Rey, S.J. ``Spatial analysis of regional economic growth,
	inequality and change." In  M.F. Goodchild and D.G. Jannelle (eds.)
	\emph{Spatially Integrated Social Science}. Oxford University Press:
	Oxford. Pages 280-299.
\item[2004] Rey, S.J. ``Spatial dependence in the evolution of regional income
	distributions." In  A. Getis, J. M\'ur and H.  Zoeller (eds.)
	\emph{Spatial Econometrics and Spatial Statistics.} Palgrave,
	Hampshire. Pages 194-213.
\item[2004] Rey, S.J. and B. D. Montouri ``U.S. regional income convergence: A
  spatial econometric perspective." In P. Cheshire and G. Duranton
  (eds.) \emph{Recent Developments In Urban And Regional Economics}. Edward
  Elgar. Pages 389-404. (Reprint of Rey and Montouri 1999).
\item[2004] Franklin, J., C. Coulter and S.J. Rey ``Change in southern
  California chaparral community over 70 years related to fire history.''
  \emph{Journal of Vegetation Science}.  15: 701-710.
\item[2003] Florax, R.J.G.M, H. Folmer and S.J. Rey. ``Specification searches
	in spatial econometrics: The relevance of Hendry's econometric
	methodology." \emph{Regional Science and Urban Economics}. 33:
	557-579.
\item[2003] Jerret, M.J., S.J. Rey, C. Dufournaud and D. Jones. ``Measuring
	the environmental ``bottom line" along the U.S.-Mexico border:
	Accounting framework and cases from the San Diego-Tijuana Region"
	\emph{Annals of the Association of American Geographers}. 93: 67-88.
\item[2002] Rey, S.J., M. Janikas, D. Larson and J.C. Snapp-Cook.  ``Subject
	and author indexes to 2001 regional science and related journal
	literature.'' \emph{The International Regional Science Review}.  25:
	331-440.
\item[2002] Anselin, L. and S.J. Rey (Editors) \emph{New Tools for for Spatial
	Data Analysis: Proceedings of a Workshop}. Center for Spatially
	Integrated Social Sciences. Santa Barbara. 
\item[2002] LeSage, J.P. and S.J. Rey. ``Restrictions in Integrated
	Econometric+Input-Output Modeling." \emph{Trade, Networks and
	Hierarchies: Modeling Regional and Interregional Economies}. In
	Geoffrey J.D. Hewings, Michael Sonis and David E. Boyce (eds.)
	Springer-Verlag. Pages  251-266.
\item[2002] Jerrett, M., S.J. Rey, C. Dufournaud, and D. Jones.
	``Environmental accounting along the U.S.-Mexican border.'' In P.
	Ganster (ed.) \emph{The U.S.-Mexican Border Environment: Economy and
	Environment for a Sustainable Border Region: Now and in 2020}. San
	Diego State University Press. San Diego. 103-141.
\item[2002] Clement, N., S.J. Rey, N.A. Fuentes and A. Brugu\'es. ``The
	U.S.-Mexican border economy in the NAFTA era: Implications for the
	environment.'' In P.  Ganster (ed.) \emph{The U.S.-Mexican Border
	Environment: Economy and Environment for a Sustainable Border Region:
	Now and in 2020}. San Diego State University Press. San Diego. 55-70.
\item[2001] Rey, S.J.,  D. Larson,  M. Janikas and Y.S. Kim.  ``Subject and
	author indexes to 2000 regional science and related journal
	literature.'' \emph{The International Regional Science Review}.  24:
	345-410.
\item[2001] Rey, S.J. ``Mathematical Models in Human Geography." In N.J.
	Smelser and P.B. Baltes (eds.) \emph{International Encyclopedia of the
	Social \& Behavioral Sciences}. 14: 9393-9399. Pergamon, Oxford.
\item[2001] Rey, S.J. ``Spatial empirics for regional economic growth and
	convergence." \emph{Geographical Analysis}. 33 (3): 195-214.
\item[2001] Isserman, A.M., K. Mera, S.J. Rey, and M.C. Waters. ``A portrait
	in four encounters: William Alonso". \emph{International Regional
	Science Review}. 24: 293-301.
\item[2000] Rey, S.J.  ``Integrated regional econometric+input-output
	modeling: Issues and opportunities."  \emph{Papers in Regional
	Science} 79: 271-292.
\item[2000] Rey, S.J. and L. Anselin. ``Regional science publication patterns
	in the 1990's." \emph{International Regional Science Review} 23:
	323-344
\item[2000] Anselin, L., S.J. Rey  and  E. Talen ``The expanded and revised
	IRSR subject and author index." \emph{International Regional Science
	Review} 23: 345-443.
\item[1999] Rey, S.J.  and R.W.  Jackson. ``Labor productivity and regional
	econometric+input-output models."  \emph{Environment and Planning A}
	31: 1583-1599. 
\item[1999] Rey, S.J. and B.D. Montouri. ``U.S. regional income convergence: A
	spatial econometric perspective." \emph{Regional Studies} 33: 145-156.
\item[1998] Rey, S.J., P. Ganster, G. del Castillo, J. Alvarez, K.
	Shellhammer, A. Sweedler and N. Clement. ``The San Diego-Tijuana
	Region." In J. Wilke and C.E. Smith (eds.) \emph{Integrating Cities
	and Regions: NAFTA and the Caribbean Face Globalization}.  UCLA
	Program on Mexico, Los Angeles.
\item[1998] Rey, S.J. ``The performance of strategies for integrating regional
	econometric and input-output models."  \emph{The International
	Regional Science Review} 20: 1-36.
\item[1997] Rey, S.J. ``Integrating regional econometric and input-output
	models: An evaluation of embedding strategies." \emph{Environment and
	Planning A} 29: 1057-1072.
\item[1997] Rey, S.J.  ``Coefficient change in integrated
	econometric+input-output models at the regional scale." \emph{Economic
	Systems Research} 9: 307-339.
\item[1997] Rey, S.J. and B. Dev. ``Integrating regional econometric and
	input-output models in a multiregional context."  \emph{Growth and
	Change} 28: 222-243.
\item[1997] Anselin, L. and S.J. Rey.  ``Introduction to the special issue on
	spatial econometrics." \emph{International Regional Science Review}
	20: 1-7.
\item[1995] Florax, R.J.G.M. and S. Rey. ``The impact of misspecified spatial
	interaction structure in regression models.`` In In L.  Anselin and
	R.J.G.M. Florax (eds.) \emph{New Directions in Spatial Analysis}.
	Springer Verlag, Berlin.
\item[1991] Anselin, L. and S. Rey.  ``Properties of tests for spatial
	dependence in linear regression models." \emph{Geographical Analysis}
	23: 112-131.
\item[1990] Anselin, L., S.J. Rey and U. Deichmann. ``The implementation of
	integrated models in small regions." In L. Anselin and M. Madden eds.
	\emph{New Directions in Regional Analysis: Integrated and
	Multiregional Approaches}.  Belhaven, London.
\item[1989] Anselin, L. and S. Rey. ``Issues in the specification of an
	integrated multiregional model for a system of small regions."
	\emph{Sistemi Urbani} 2: 177-201.

\item[\textbf{Book Reviews}]
\item[2000] Rey, S.J. \emph{Econometric Advances in Spatial Modelling and
	Methodology: Essays in Honour of Jean Paelinck}. Edited by Daniel A.
	Griffith, Carl G.  Amrhein and Jean-Marie Huriot. In \emph{Regional
	Science and Urban Economics}.
\item[1997] Clement, N.C. and S.J. Rey.  \emph{Border-Regional Economics.} By
	Rogxing Guo. In \emph{Journal of Borderland Studies}, 12: 175-179.

 \item[\textbf{Technical Reports}]
 \item[2010] Rey, S.J. and L. Anselin. Spatial Linkages and Urban Economic Development.
   Economic Development Administration, U.S. Department of Commerce.
\item[2005] Rey, S.J., J.C. Duque, O. Smirnov, Y. Kim, and P. Stephens.
  Identifying Value-Added Industry Clusters in San Diego County. Regional
  Analysis Laboratory Technical Report: REGAL 050615.
\item[2005] Rey, S.J., J.C. Duque, O. Smirnov, Y. Kim, and P. Stephens.
  Geocoding the Connectory. Regional Analysis Laboratory Technical Report:
  REGAL 050627.
\item[2003] Rey, S.J. ``Identifying Regional Industrial Clusters in Imperial
	County California.''  California Center for Border and Regional
	Economic Studies.
\item[2001] Rey, S.J. ``Identifying Regional Industrial Clusters in
	California: Volume V Sub-state Results.'' California Employment
	Development Department. Sacramento. (September). 
\item[2000] Rey, S.J.  ``Identifying Regional Industrial Clusters in
	California: Volume IV The Role of Industry Clusters in California's
	Recent Economic Expansion.'' California Employment Development
	Department. Sacramento. 
\item[2000] Rey, S.J. ``Identifying Regional Industrial Clusters in
	California: Volume III Technical Documentation of the Candidate
	Statewide Industry Clusters.'' California Employment Development
	Department. Sacramento.
\item[2000] Rey, S.J. ``Identifying Regional Industrial Clusters in
	California: Volume II A Methods Handbook.'' California Employment
	Development Department. Sacramento. 
\item[2000] Rey, S.J. and D.  Mattheis. ``Identifying Regional Industrial
	Clusters in The California Economy: Volume I Conceptual Design."
	California Employment Development Department. Sacramento. 
\item[2000] Butler, M., S. Rey and G. Singh ``Workforce Issues of the Visitor
	Cluster of San Diego.'' Technical Report to the San Diego Workforce
	Partnership. 
\item[2000] Sciglimpaglia, D., S. Rey, M. Butler and G. Singh ``Workforce
	Issues of the Computer and Electronics Manufacturing Cluster of San
	Diego.'' Technical Report to the San Diego Workforce Partnership. 
\item[2000] Singh, G. and S. Rey ``Workforce Issues of the Biosciences Cluster
	of San Diego.''  Technical Report to the San Diego Workforce
	Partnership.
\item[1998] Rey, S.J. ``Technician Needs Assessment Survey." Report to the San
	Diego Regional Economic Development Corporation. 
\item[1997] Rey, S.J. and N. Clement. ``Estimates of Employment and Income
	Impacts of the Space and Naval Warfare Systems Command (SPAWAR)
	Operations in the San Diego Region." Report to the San Diego State
	Foundation Defense Conversion Center. 
\item[1996] Gerber, J., D. Gupta, and S. Rey, ``The Impacts of the San Diego
	State University on the Regional Economy." Office of the Vice
	President for Academic Affairs, San Diego State University. 
\item[1995] Rey, S. ``A Decompositional Analysis of Defense Dependent
	Industrial Clusters." Report to the San Diego State Foundation Defense
	Conversion Center. 
\item[1995] Rey S.  ``The Impacts of Defense Conversion on the San Diego
	Economy." Report to the San Diego State Foundation Defense Conversion
	Center. 
\item[1995] Rey, S. ``An Evaluation of the Demographic and Economic
	Forecasting Model." Report to the San Diego Association of
	Governments. 
\item[1995] Rey, S. and N.  Clement ``The San Diego Economic Information and
	Modeling Project." Report to the San Diego State Foundation Defense
	Conversion Center.
\item[1991] Anselin, L. and S. Rey (1991) ``The Performance of Tests for
	Spatial Dependence in a Linear Regression." National Center for
	Geographic Information and Analysis Technical Paper 91-13. 
\item[1988] Rey, S. ``Data Issues in the Development of Integrated
	Multiregional Models." Community and Organization Research Institute
	Working paper WRC700-2, U.C. Santa Barbara. 
\item[1987] Anselin, L., P.  Krsnak and S. Rey.  ``Economic Impacts of the
	University of California Santa Barbara on the Region." Interim Report
	to UCSB. 
\item[1987] Anselin, L., P. Krsnak and S. Rey. ``Economic Impacts of the
	University of California Santa Barbara on the Region: An Input-Output
	Analysis." Interim Report to UCSB. 
\item[\textbf{Proceedings}]
\item[1996] Clement, N. and S.J. Rey, ``The San Diego-Tijuana Region."
	Transnational Regional Economic Development - North America,
	Proceedings, 15-19.
\item[1996] Frank, B., R. Wright, and S.J. Rey, ``Linking Preference Analysis
	Techniques and GIS for Fire Fuel Management." GIS/LIS 96' Proceedings,
	1124-1140.
\end{cvlist}

\begin{cvlist}{Invited Lectures}
\item[2014] Rey, S.J. ``Space-time empirics.'' School of Geographic Sciences
  and Urban Planning, Arizona State University. January.
\item[2013] Rey, S.J. ``Spatio-temporal analytics for socioeconomic
  processes.'' School of Environmental \& Public Affairs, University of
  Nevada, Las Vegas. April.
\item[2013] Rey, S.J. ``Exploratory space-time data analysis: Distributional
  and computational issues.'' CyberGIS Speaker Series. University of Illinois,
  Urbana-Champaign. February.
\item[2012] Rey, S.J. ``Open source spatial data analysis: Lessons for
  education and research from PySAL.'' Keynote, Open Source Geospatial
  Research and Education Symposium. Yverdon-les-Bains, Switzerland. October.
\item[2012] Rey, S.J. ``Markov based methods for spatial dynamics.''
  Department of Geography, University of Zurich. October.
\item[2012] Rey, S.J. ``Exploring spatial dynamics of neighborhoods.''
  Spatial Structures for the Social Sciences. Brown University. March.
\item[2011] Rey, S.J. ``Recent advances in Software for Space-Time Data
  Analysis.'' Future Directions in Spatial Demography, Specialist Meeting.
  Santa Barbara. December.
\item[2011] Rey, S.J. ``Exploratory space-time data analytics.'' Plenary
  Speaker. GEOINT, San Antonio. October.
\item[2010] Rey, S.J. ``New approaches for exploratory space-time analysis
  (ESTDA).'' School of Geography and Development, University of Arizona.
  December.
\item[2010] Rey, S.J. ``New approaches to exploratory space time data
  analysis.'' Arthur Getis Lecture in Spatial Analysis. Department of
  Geography, San Diego State University. October.
\item[2010] Rey, S.J. ``Markov based measures of spatial dynamics.''
  Institute for Economic Geography and GIScience, Vienna University of
  Economics and Business. June.
\item[2008] Rey, S.J. ``Exploratory Analysis of Space-Time Data.'' 
  Regional Research Institute, West Virginia University. March.
\item[2008] Rey, S.J. ``Show Me the Code: Spatial Analysis and Open Source.''
  Department of Geography, San Diego State University. January.
\item[2007] Rey, S.J. ``Exploratory Analysis of Space-Time Data.'' 
  Survey Research Center, University of California, Berkeley.  November.
\item[2007] Rey, S.J. ``Exploratory Analysis of Space-Time Data.'' Department
	of Geography Colloquia, University of Southern California.  March.
\item[2004] Rey, S.J. ``STARS: Space-Time Analysis of Regional Systems.''
  ESRI-University of Redlands Colloquia. September.
\item[2004] Rey, S.J. ``Regional science in the Borderlands: Research and
  public policy opportunities.'' Departments of Geography and Planning,
  Arizona State University. March.
\item[2004] Rey, S.J. ``Exploratory space-time data analysis of socioeconomic
	processes.'' Symposium on Spatial Information Science for Human and
	Social Sciences. University of Tokyo. January.
\item[2003] Rey, S.J. ``Python for exploratory space-time data analysis.''
	Center for Spatially Integrated Social Sciences, University of
	California, Santa Barbara. October.
\item[2003] Rey, S.J. ``Exploratory space-time analysis of regional income
	evolutions.'' Quantitative Methods in Social Science Program
	Colloquia. University of California, Santa Barbara. October.
\item[2003] Rey, S.J. ``San Diego State University and the Regional
	Economy.'' University of Limerick Executive MBA Workshop. August.
\item[2003] Rey, S.J. ``Identifying Industrial Clusters in the Imperial County
	Economy.'' California Center for Border and Regional Economic Studies.
	May.
\item[2003] Rey, S.J. ``The use of Python for Geocomputation and
	Geovisualization.'' SANDPYT: San Diego Python Users Group. May.
\item[2002] Rey, S.J. ``Exploratory Spatial Data Analysis of Regional Economic
	Change.'' Regional  Science Program, University of Illinois, Urbana.
	May. 
\item[2001] Rey, S.J. ``Spatial Effects in the Analysis of Regional Income
	Convergence and Inequality." School of Economics, University of
	Queensland. October.
\item[2001] Rey, S.J.``New Spatial Empirics for Regional Inequality and
  Growth.'' The Tod Spieker Colloquium. Department of Geography, University of
  California, Los Angeles. May. 
\item[2000] Rey, S.J. ``STARS: Space-Time Analysis of Regional Systems, An
	Open-Source Approach to Spatial Analysis.'' Center for Spatially
	Integrated Social Sciences, UC Santa Barbara. December. 
\item[2000] Rey, S.J. ``Industry Clusters in California: Sub regional
	analytical issues." Presentation to the Director's Office, California
	Employment Development Department.  October. economic economic 
\item[2000] Rey, S.J. ``Identifying Regional Industry Clusters in
	California.'' Advisory Committee, California Employment Development
	Department. April. 
\item[1999] Rey, S.J. ``Space-Time Analysis of Regional Systems: STARS.''
	Center on Computational Science and Engineering. San Diego State
	University. December. 
\item[1999] Rey, S.J. ``Spatial Analysis of Regional Growth Dynamics.''
	Department of Geography, University of California at Santa Barbara.
	December.
\item[1999] Rey. S.J. ``Spatial Markov Modeling of Regional Convergence.''
	Regional Science Program, University of Illinois, Urbana. November. 
\item[1998] Rey, S.J. ``U.S. Regional Income Convergence: A Spatial
	 Econometric Perspective.'' The Tinbergin Institute. Amsterdam,
	 Netherlands. November. 
\item[1998] Rey, S.J.  ``Multiregional Economic Modeling in the US" Seminar,
	Department of Regional Economics, Universidad Autonoma Coahuila,
	Coahuila, Mexico, April. 
\item[1997] ``Recent Advances in Regional Economic Modeling" Seminar,
	Department of Economics, San Diego State University, March.
\item[1996] Rey, S.J. and N.C. Clement. ``Regional Economic Modeling in
	Support of Economic Development." Annual Conference of the California
	State University Auxiliary Organization Association, San Diego,
	January. 
\item[1995] Rey, S.J. ``The San Diego Economic Information and Modeling
	Project." San Diego Technology Council, San Diego, CA, May. 
\item[1995] Weeks, J. and S.J. Rey. ``The Results of a Survey of Small Defense
	Related Firms in San Diego County" The Californias in Transition
	Seminar, San Diego State University, May. 
\item[1995] Rey, S.J. ``Recent Advances in Regional Socioeconomic Modeling."
	San Diego Association of Governments, San Diego, CA, April. 
\item[1994] Rey, S.J. ``Integrated Multiregional Modeling for Systems of Small
	Regions." The Californias in Transition Seminar, San Diego State
	University, May.
\item[1991] Rey, S.J. ``The Spatial Dimensions of Growth Control Analyses."
	Colloquium, Department of Geography San Diego State University,
	December 1991.  \end{cvlist}

\begin{cvlist}{Conference Participation and Presentations}
\item[2013] Rey, S.J. and J. Laura. ``Parallel PySAL.'' CyberGIS All-Hands
  Meeting. Seattle, September.
\item[2013] Rey, S.J. ``Code as text: Open source in academia.'' Scientific
  Computing with Python. Austin, July.
\item[2013] Rey, S.J., L. Anselin and J. Laura. ``Spatial analysis and big 
  data: Challenges and opportunities.'' SIAM Conference for Computational 
  Science and Engineering. Boston, MA. February.
\item[2013] Mack, E.A. and S.J. Rey. ``An econometric approach to evaluate 
  regional variations in broadband linkages to knowledge intensive firms.'' 
  Western Regional Science Association. Santa Barbara, CA. February.
\item[2013] Rey, S.J. ``Fast algorithms for a space-time concordance 
  measure.'' Western Regional Science Association. Santa Barbara,
  CA. February.
\item[2012] Murray, A.T., T. Grubesic, S.J. Rey and L. Anselin. ``Spatial data
  uncertainty and cluster detection.'' GIScience.
  Columbus,Ohio. September.
\item[2012] Rey, S.J. ``Exploratory space-time data analysis''. GIScience,
  Columbus,Ohio. September.
\item[2012] Rey, S.J., X. Li, and L. Anselin. ``Visualization of Space-Time 
  Dynamics in Criminal Activity.'' Joint Statistical Meetings. San Diego. 
  July.
\item[2012] Anselin, L. and S.J. Rey.``Spatial Econometrics in an Age of
  CyberGIScience.'' Joint Statistical Meetings. San Diego. July.
\item[2012] Rey, S.J. ``PySAL: A Python library for exploratory spatial data
  analysis and geocomputation.'' Scientific Computing with Python. Austin,
  July.
\item[2012] Smith, R., and S.J. Rey. Decomposing the Gini Coefficient to 
  Measure the Inequality of Places. Presented at the Sentinels of 
  Sustainability, Rio+20 United Nations Conference on Sustainable Development. 
  Fort Leme, Rio de Janeiro, Brazil: Federal University of Rio de Janeiro. 
  June.
\item [2012] Anselin, L. and S.J. Rey. ``Spatial Econometrics in an Age of
  CyberGIScience.'' Association of American Geographers. New York. February.
\item [2012] Kleinschmidt. S., A.T. Murray, S.J. Rey, T.H. Grubesic. ``Spatial
  patterns and geographical data uncertainty.'' Association of American Geographers. New York. February.
\item [2012] Rey, S.J., L. Anselin, R. Pahle, and X. Kang. ``Parallelizing
  PySAL.'' Association of American Geographers. New York. February.
\item [2012] Rey, S.J., E. Mack, and J. Koschinsky. ``Exploratory space-time
  analysis of burglary patterns.'' Western Regional Science Association.
  Lihue, February.
\item [2011] Folch, D.C. and S.J. Rey. ``The Centralization Index as a Tool
  for Measuring Local Segregation.''  
  Regional Science Association International. Miami, November.
\item [2011] Guitierrez, M.S. and S.J. Rey. ``Spatial Economics of Convergence
  in Mexico.''   
  Regional Science Association International. Miami, November.
\item [2011] Rey, S.J. ``Rank Based Markov Measures of Regional Income Distribution
  Dynamics''. Regional Science Association International. Miami, November.
\item [2011] Rey, S.J. and L. Anselin ``PySAL: Python Spatial Analysis
  Library''. CyberGIS All Hands Meeting. Oak Ridge National Laboratory.
  September.
\item [2011] Rey, S.J., L. Anselin, D.C. Folch. ``PySAL: Python Spatial
  Analysis Library 2.0.''
  Association of American Geographers. Seattle, April.
\item [2011] Rey, S.J. ``Space-time analysis of regional systems.''
  Association of American Geographers. Seattle, April.
\item[2011] Rey, S.J., A.T. Murray and L. Anselin. ``Visualizing regional
  income distribution dynamics.'' Western Regional Science Association.
  Monterey,  March.
\item[2010] Rey, S.J. and L. Anselin. ``Spatial econometrics with PySAL and
  GeoDaSpace''. Regional Science Association International. Denver, November.
\item[2010] Sastr\'e-Guti\'errez, M.L. and S.J. Rey. ``Spatial econometrics of
  convergence in Mexico''. Regional Science Association International. Denver, November.
\item[2010] Sastr\'e-Guti\'errez, M.L. and Rey, S.J. ¿Spatial Socioeconomic Mobility in Mexico¿, 
XX Coloquio Mexicano de Econom\'ia Matem\'atica y Econometr\'ia, Guanajuato, M\'exico, 
September.
\item[2010] Anselin, L., S.J. Rey and A. Winslow. ``New tools for statistical
  point pattern analysis on networks with large datasets.'' Com.Geo.
  Washington, D.C.. June.
\item[2010] Anselin, L., S.J. Rey and J. Koschinsky. ``Flexible geospatial
  visual analytics and simulation technologies.'' National Institute of
  Justice Conference. Arlington. June.
\item[2010] Rey, S.J. and L. Anselin ``PySAL: A Python library for spatial
  analysis and geocomputation.'' Association of American Geographers.
  Washington, D.C.. April.
\item[2010] Murray, A.T., Y. Liu, S.J. Rey and L. Anselin. ``Exploring movement
  object patterns.'' Western Regional Science Association. Sedona, February.
\item[2010] Rey, S.J., L. Anselin, D.C. Folch, D. Arribas-Bel, M.L. Sastr\'e
  Guti\'erez and L. Interlante. ``Measuring spatial dynamics in metropolitan
  areas.'' Western Regional Science Association. Sedona, February.
\item[2010] Sastr\'e-Guti\'errez and S.J. Rey. ``Spatial socioeconomic mobility in Mexico.''
Western Regional Science Association. Sedona, February.
\item[2010] Ye, Xinyue and S.J. Rey. ``Space-time empirics for economic
  growth.'' Western Regional Science Association. Sedona, February.
\item[2009]  Murray, A., P.D. Padegimas, L. Anselin, S.J. Rey and P. Gober.
  ``A spatial optimization model for water supply allocation.'' North American
  Meetings of the Regional Science Association International. San Francisco,
  November.
\item[2009]  Sastr\'e Guti\'erez, M.L. and S.J. Rey. ``Spatial income mobility
  in Mexico.'' North American Meetings of the
  Regional Science Association International. San Francisco, November.
\item[2009] Rey, S.J., L. Anselin, D.C. Folch, D. Arribas-Bel, M.L. Sastr\'e
  Guti\'erez and L. Interlante. ``Measuring spatial dynamics in metropolitan
  areas.'' North American Meetings of the Regional Science Association
  International. San Francisco, November.
\item[2009] Rey, S.J., L. Anselin, D.C. Folch, D. Arribas-Bel, M.L. Sastr\'e
  Guti\'erez and L. Interlante. ``Spatial linkages and urban economic development''
  Economic Development Adminstration Research Symposium. Morgantown, October.
\item[2009] Rey, S.J. and D.C. Folch. ``What Can 70 Million or So Neighborhoods
  Tell Us about the Performance of Income Segregation Measures?'' Spatial
  Economerics Association. Barcelona, July.
\item[2009] Rey, S.J. and L. Anselin. ``PySAL: Python Library for Spatial Analytical Functions.''
  Association of American Geographers. Las Vegas. March.
\item[2009] Rey, S.J., L. Anselin and M. Hwang. ``Dynamic manipulation of
  spatial weights using web services.'' Western Regional Science
  Association. Napa, February.
\item[2009] Elias, M. and S.J. Rey. ``Educational performance and spatial
  convergence in Peru: 1993-2005.  Western Regional Science
  Association. Napa, February.
\item[2009] Schmidt, C.R., S.J. Rey and A. Skupin. ``Effects of regular
  topology in spherical self-organizing maps.'' Western Regional Science
  Association. Napa, February.
\item[2009] Duque, J.C., L. Anselin and S.J. Rey. ``The max-p region
  problem.'' First Conference of the Regional Science Association of the
  Americas. Cartagena, February.
\item[2008] Rey, S.J. ``20 Years of Spatial Econometrics''. 	Panel Member.
  Regional Science Association International. Brooklyn. November.
\item[2008] Duque, J.C., S.J. Rey and C.R. Schmidt ``INCLUSIO: New ways to
  explore interindustry relationships.''Regional Science Association International. Brooklyn. November.
\item[2008] Schmidt, C.R., S.J. Rey and A. Skupin ``PySOM: A Graph Based
  Implementation of Self-Organizing Maps.'' Regional Science Association International. Brooklyn. November.
\item[2008] Rey, S.J. and B. Dev  ``Identifying patterns of change in income
  inequality across geographic areas.'' Regional Science Association International. Brooklyn. November.
\item[2008] Rey, S.J. and X. Ye  ``Distributional Properties of LISA Time
  Paths.'' Regional Science Association International. Brooklyn. November.
\item[2008] Sergio Rey and David Folch 	``A spatiotemporal approach to the
  measurement of economic segregation.'' Spatial Econometrics Association.
  Brooklyn. Novermber.
\item[2008] Schmidt, C., Rey, S.J. and A. Skupin. ``Effects of Irregular Topology in Spherical
  Self-Organizing Maps.'' Association of American Geographers. Boston. March.
\item[2008] Rey, S.J. and X. Ye.  ``Dynamic Pseudo Weighted Voronoi:
  Integrating Geographic and Attribute Spaces.'' Association of American Geographers. Boston. March.
\item[2008] Stephens, P. and S.J. Rey ``Spatial Analysis Of HUBZone
  Determinations In California Metro Areas.''  	Association of American
  Geographers. Boston. March.
\item[2008] Rey, S.J. and X. Ye. ``Comparative spatial dynamics of regional
  systems'. Western Regional Science Association. Kona, HI. February.
\item[2007] Rey, S.J. and X. Ye. ``Comparative space-time dyanmics: China and
  the US 1989-2000''. Regional Science Association International. Savannah, GA.
  November.
\item[2007] Rey, S.J. and J. Le Gallo ``Spatial analysis of economic
  convergence''. Regional Science Association International. Savannah, GA.
  November.
\item[2007] Rey, S.J. and M. Sastr\'e Guti\'errez ``Interregional Inequality
  Dynamics in in Mexico''. Regional Science Association International. Savannah, GA.
  November.
\item[2007] Rey, S.J. and X. Ye.
``Exploring spatial dynamics in city size distributions.''.
	The 2nd ICA Workshop on Geospatial Analysis and Modeling - Spatial
	Structure and Dynamics of Urban Environments. 
	Athens, Ga. July.
\item[2007] Sastr\'e Guti\'errez, M. and S.J. Rey ``Spatial income mobility in
  Mexico.'' Encuentro Nacional Sobre Desarrollo Regional en Mexico, AMECIDER.
  July.
\item[2007] Rey, S.J. ``Show me the code: Open source and spatial analysis.''
	Association of American Geographers. San Francisco. April.
\item[2007] Rey, S.J. and X. Ye ``Exploratory Comparative Spatial
	Dynamics:Integrating Computational Geometry with ESTDA.'' Association
	of American Geographers. San Francisco. April.
\item[2007] Stephens, P. and S.J. Rey ``Spatial Analysis of HUBZone
	Designations in San Diego, California.'' Association of American
	Geographers. San Francisco. April.
\item[2006] Rey, S.J., L. Anselin, J.C. Duque and X. Li ``Max p-region based
    estimation of disease rates.'' Regional Science Association International
    Meetings. Toronto. November.
\item[2006] Rey, S.J. and X. Ye ``Exploring spatial dynamics in city size
    distributions.'' Regional Science Association International
    Meetings. Toronto. November.
\item[2006] Rey, S.J. ``An exploratory space-time data analysis toolkit for
	the social sciences.'' National Science Foundation, Human and Social
	Dynamics Principal Investigators Meeting. Washington D.C. September.
\item[2006] Anselin, L. and S.J. Rey ``PySAL: A Python Library for Spatial
	Analysis.'' Joint Statistical Meetings. Seattle. August.
\item[2006] Anselin, L. and S.J. Rey ``Perspectives on spatial data analysis:
  the contributions by Arthur Getis to the field.''
 Association of American Geographers. Chicago. April.
\item[2006] Hamada, Y., D.A. Stow, S.J. Rey and L. Coutler ``Methods for assessing thematic accuracy
  of classification maps derived from remotely sensed imagery.''
 Association of American Geographers. Chicago. April.
\item[2006] Janikas, M.V. and S.J. Rey ``Assessing relative distributions in
  the presence of spatial dependence.''
 Association of American Geographers. Chicago. April.
\item[2006] Rey, S.J. and X. Ye. ``Comparative space-time dynamics''
 Association of American Geographers. Chicago. April.
\item[2005] Rey, S.J. and B. Dev. ``Identifying trends of $\sigma$-convergence
  in the presence of dynamic spatial effects.''
 Regional Science Association International. Las
  Vegas. November.
\item[2005] Rey, S.J., J.C. Duque and L. Anselin. ``Clustering components in
  the Python Spatial Analysis Library (PySAL). 
 Regional Science Association International. Las
  Vegas. November.
\item[2005] Rey, S.J., O. Smirnov, J.C. Duque, P. Stephens and Y.S. Kim.
  ``Regional analysis in support of economic development.'' 
 Regional Science Association International. Las
  Vegas. November.
\item[2005] Rey, S.J., M.V. Janikas and O. Smirnov. ``Exploratory
  geovisualization of spatial income dynamics.'' Regional Science Association International. Las
  Vegas. November.
\item[2005] Janikas, M.V. and S.J. Rey ``A confirmatory approach for the
  evaluation of the effects of spatial clustering and inequality on economic
  growth in the United States: 1969-20001.'' Regional Science Association International. Las
  Vegas. November.
\item[2005] Duque, J.C. and S.J. Rey ``Network based approaches towards
  industrial clustering.'' Regional Science Association International. Las
  Vegas. November.
\item[2005] Rey, S.J., M.V. Janikas and O. Smirnov. ``Exploratory geovisualization
  of spatial dynamics.'' Geocomputation 2005. University of Michigan. August.
\item[2005] Anselin, L. and S.J. Rey ``PySAL a Python library for spatial analytical
  functions.'' Geocomputation 2005. University of Michigan. August.
\item[2005] Rey, S.J. ``STARS: Space-Time Analysis of Regional Systems.''
  Workshop on Spatial Econometrics. Kiel Institute for World Economics, Kiel
  Germany. April.
\item[2005] Anselin, L. and S.J. Rey ``PySAL, a Python Library for Spatial
  Analytical Functions''. Association of American Geographers. Denver, CO.
  April.
\item[2005] Rey, S.J. and M.V. Janikas ``STARS: Space-Time Analysis of
  Regional Systems.'' Western Regional Science Association. San Diego, CA.
  February.
\item[2004] Janikas, M.V. and S.J. Rey ``Spatial Clustering, Inequality and
  Income Convergence.'' Regional Science Association International. Seattle,
  WA. November.
\item[2004] Rey, S.J. and M.V. Janikas ``Exploratory space-time data analysis
  with STARS.'' Association of American Geographers. Philadelphia, PA. March.
\item[2004] Rey, S.J. and B. Dev ``$\sigma$-convergence in the presence of
	spatial effects.'' Western Regional Science Association. Maui, HA.
	February.
\item[2003] Rey, S.J. and M.V. Janikas ``Convergence and space.''Regional
	Science Association International. Philadelphia, PA.  Novermber.
\item[2003] Rey, S.J., M.V. Janikas, B. Dev and Y.S. Kim ``Exploratory
	space-time analysis with STARS.'' Regional Science Association
	International. Philadelphia, PA. Novermber.
\item[2003] Rey, S.J., D.J. Mattheis and Y.S. Kim ``Building Consensus
	Clusters: An evaluation of industrial cluster identification
	strategies'' Regional Science Association International. Philadelphia,
	PA. Novermber.
\item[2003] Kim, Y.S. and S.J. Rey ``The aerospace industry cluster in
	California.'' Regional Science Association International.
	Philadelphia, PA. Novermber.
\item[2003] Rey, S.J., M.V. Janikas, B. Dev and Y.S. Kim ``Exploratory
	space-time data analysis with Python.'' Python for Scientific
	Computing Workshop. Pasadena, CA. September.
\item[2003] Rey, S.J., D.J. Mattheis and Y.S. Kim ``Regional Industrial
	Clusters in California: An Application of Consensus Clustering.''
	Western Regional Science Association Meetings.  Rico Rico, AZ. March.
\item[2003] Rey, S.. ``Empirics for space-time information systems.''
	Space-Time Information Systems 2003. University of Michigan, January. 
\item[2002] Rey, S.J. ``STARS: Space-time Analysis of Regional Systems". North
	American Meeting of the Regional Science Association International.
	San Juan, Puerto Rico. November.
\item[2002] Rey, S.J., G.R. West and M.V. Janikas ``Uncertainty in integrated
	regional models". North American Meeting of the Regional Science
	Association International.  San Juan, Puerto Rico. November.
\item[2002] Anselin, L. and S.J. Rey (Organizers). \emph{New Tools for Spatial
	Data Analysis.} Center for Spatially Integrated Social Sciences
	Specialist Meeting. Santa Barbara, Ca. May 10-11.
\item[2002] Rey, S.J. ``Spatial analysis of regional income inequality."
	Western Regional Science Association Meetings. Montery, Ca.  February.
\item[2001] Rey, S.J., D.J. Mattheis and Y.S. Kim. ``Consensus industrial
	clustering." 17th Pacific Conference of the Regional Science
	Association International. Portland, Or. July. 
\item[2001] Anselin, L. and S.J. Rey. ``Open software tools for exploratory
	spatial data analysis." Association of American Geographers. New York.
	March. 
\item[2001] Rey, S.J.  ``Spatial dependence in the evolution of regional
	income distributions." Western Regional Science Association Meetings.
	Ojai, Ca. February.
\item[2000] Rey, S.J. and L. Anselin ``Regional Science Publication Patterns
	in the 1990's''. North American Meeting of the Regional Science
	Association International.  Chicago. November.
\item[2000] Clement, N.C. and S.J. Rey ``The Economic Structure of the
	US-Mexico Border Region in the NAFTA Era.'' Border Institute II. Rio
	Rico, Arizona.  April. 
\item[2000] Jerrett, M.J. and S.J. Rey ``Environmental Accounting in Border
	Regions.'' Border Institute II. Rio Rico, Arizona.  April. 
\item[2000] Rey, S.J. ``Spatial Empirics for Economic Growth and
	Convergence.'' Western Regional Science Association Meetings. Kauai.
	February. 
\item[1999] Rey, S.J. ``Integrated Regional Econometric+Input-Output
	Modeling: Issues and Opportunities.'' North American Meeting of the
	Regional Science Association International.  Montreal. November. 
\item[1999] LeSage, J.P. and S.J. Rey ``Restrictions in Integrated
	Econometric+input-output modeling.'' North American Meeting of the
	Regional Science Association International.  Montreal. November. 
\item[1999] Florax, R.J.G.M., E. Lopez-Bazo and S.J. Rey.  ``Spatial economic
	growth: What do we know?'' European Congress of the Regional Science
	Association International. Dublin, Ireland.  August. 
\item[1999] Rey, S.J. ``Space in integrated econometric and input-output
	models.'' Southern Regional Science Association Meetings. Richmond,
	VA. April. 
\item[1999] Rey, S.J. and D.  Mattheis. ``An evaluation of methods for
	identifying regional industrial clusters.'' Annual meetings of the
	Association of American Geographers, Honolulu, HA. 
\item[1998] Rey, S.J. and M.G. Boarnet. ``A taxonomy of spatial econometric
	models for simultaneous equations systems.'' North American Meeting of
	the Regional Science Association International.  Santa Fe, New Mexico.
	November. 
\item[1998] Rey, S.J. ``Methodological Issues in the Integration of Regional
	Econometric and Input-Output Models." Paper presented at the Community
	Planning and Analysis Network Meeting, Santa Fe, NM, November. 
\item[1998] Rey, S.J. and N.C.  Clement, ``The San Diego Economic Information
	and Modeling Project." Network of Border Economists, El Paso, Texas,
	April 27, 1998.
\item[1998] Rey, S.J. and B.D. Montouri. ``U.S. regional income convergence: A
	spatial econometric perspective.'' Western Regional Science
	Association Meetings. Monterey, CA. February. 
\item[1997] Rey, S.J. and R.W. Jackson. ``Labor productivity changes in
	regional econometric and input-output models.'' North American Meeting
	of the Regional Science Association International. Buffalo, N.Y.
	November.
\item[1997] Anselin, L. and S.J. Rey ``Geographic spillovers in regional
	economic models.''North American Meeting of the Regional Science
	Association International. Buffalo, N.Y. November. 
\item[1996] Rey, S.J. ``Coefficient Change in Embedded Econometric and
	Input-Output Models at the Regional Scale." Regional Science
	Association International annual meeting, Arlington Virginia November. 
\item[1996] Clement, N. and S.J. Rey. ``The San Diego-Tijuana Region."
	Transnational Regional Economic Development in North America.  Tucson,
	Arizona. May.
\item[1996] Rey, S.J., and B. Dev. ``Integrating Econometric and Input-output
	Models in a Multiregional Context." Western Regional Science
	Association annual meeting, Napa CA, February. 
\item[1995] Rey, S.J., ``The Impact of Defense Spending on the San Diego
	Region: An Integrated Modeling Analysis." Thirtieth anniversary
	conference of the Regional Research Institute, West Virginia
	University, Morgantown, W.V., November. 
\item[1995] Anselin, L. and S. Rey, ``The Elusiveness of Spatial Spillovers:
	State Fiscal Policy Interdependence Revisited." Regional Science
	Association International, annual meeting, Cincinnati, Ohio, November. 
\item[1995] Rey, S.J., ``The Performance of Alternative Integration Strategies
	for Combining Regional Econometric and Input-Output Models." Regional
	Science Association International, annual meeting, Cincinnati, Ohio,
	November. 
\item[1995] Rey, S.J., P.Ganster, G. del Castillo, J. Alvarez, K.
	Shellhammer, A. Sweedler and N.  Clement. ``The San Diego-Tijuana
	Region" Integrating Cities and Regions: NAFTA and Beyond. Vancouver,
	B.C. September. 
\item[1995] Anselin, L.  and S. Rey, ``Spatial Dependence in Models with
	Pooled Data: State Fiscal Policy Interdependence Revisited." Western
	Regional Science Association annual meeting, San Diego CA, February. 
\item[1994] Rey, S., ``The Role of Spatial Effects in the Estimation and
	Simulation of Multiregional Econometric Models." Regional Science
	Association International, annual meeting, Niagara Falls, Ontario
	Canada, November.
\item[1994] Rey, S., A. Getis, and A.  Bortman, ``Estimation of Suppressed
	Employment Data: an Evaluation of Spatial and Non-spatial Approaches."
	Regional Science Association International, annual meeting, Niagara
	Falls, Ontario Canada, November. 
\item[1994] Rey, S. and A.  Bortman, ``Integration of GIS and Regional
	Modeling: The Case of Estimating Suppressed Employment Data at the
	Sub-state Scale." Association of American Geographers, annual meeting,
	San Francisco, CA, April. 
\item[1993] Rey, S., ``Spatial Heterogeneity in Multiregional Econometric
	Models." Regional Science Association International, annual meeting,
	Houston, TX, November. 
\item[1992] Rey, S., ``Integrated Econometric and Input-output Regional
	Employment Models: An Evaluation of Alternative Approaches." Regional
	Science Association International, annual meeting, Chicago, IL,
	November. 
\item[1992] Florax, R. and S.  Rey, ``The Impacts of Misspecified Spatial
	Weight Structures in Linear Regression Models." European Congress of
	the Regional Science Association, Louvain-La-Neuve Belgium, August. 
\item[1992] Rey, S., ``Integrated Econometric and Input-output Models: An
	Analysis of Alternative Approaches.`` Association of American
	Geographers, annual meeting, San Diego, CA, April.  \end{cvlist}

\begin{cvlist}{Research Grants and Contracts}
\item[2012-13]\emph{Editorial Office. International Regional Science Review}.
	Principal Investigator.\\
	Sponsor: SAGE Publications Incorporated. (\$52,000).
\item[2011-12] \emph{Residential Segregation
  Measures and Their Spatial Properties}. Doctoral Dissertation Research.  Principal Investigator.\\
    Sponsor: National Science Foundation. (\$11,073).
\item[2010-14] \emph{CyberGIS Software Integration for Sustained Geospatial
  Innovation}. Co-Investigator.\\Sponsor: National Science Foundation
  (\$4,400,000, ASU Share \$1,275,000).
\item[2010-12] \emph{Flexibile geospatial visual analytics and
  simulation technologies to enhance criminal justice decision support
  systems}. Co-Principal Investigator.\\Sponsor: National Institute of
  Justice (\$1,500,000).
\item[2009-10] \emph{Spatial analytical framework for examining sex
  offender residency issues over space and time.} Co-Principal
  Investigator.\\Sponsor: National Science Foundation (\$235,000).
\item[2008-10] \emph{Spatial Linkages and Urban Economic Development}.
  Principal Investigator.\\
  Sponsor: Economic Development Administration, U.S. Department of Commerce
  (\$155,000).
\item[2008-11]\emph{Editorial Office. International Regional Science Review}.
	Principal Investigator.\\
	Sponsor: SAGE Publications Incorporated. (\$124,000).
\item[2008-10] \emph{Comparative Space-Time Dynamics}. Doctoral Dissertation Research.
  Principal Investigator.\\Sponser: National Science Foundation (\$1,500).
\item[2007-09] \emph{Industrial Clusters and Trade}. Sponsor: Department of
	Education (Subcontract) (\$40,000).
\item[2006-07] \emph{Comparative Regional Income Dynamics: Clustering, Scale,
  and Geocomputation}. Doctoral Dissertation Research.
  Principal Investigator.\\Sponser: National Science Foundation (\$4,200).
\item[2006-07] \emph{Regional Socieconomic Modeling in Support of Economic
  Development Networks.} Co-Principal Investigtor.\\ Sponsor: Defense
  Logistics (\$900,000).
\item[2005-06] \emph{Regional Socieconomic Modeling in Support of Economic
  Development Networks.} Co-Principal Investigtor.\\ Sponsor: Defense Logistics
  Agency (\$1,200,000).
\item[2004-07] \emph{An Exploratory Space-Time Data Analysis Toolkit for
  Spatial Social Science Research}. Principal Investigator.\\Sponsor: National
  Science Foundation. (\$97,000)
\item[2004-06] \emph{Prostate Cancer ESDA and Spatial Statistics}. Co-Principal
	Investigator.\\Sponsor: Association of
	Teachers of Preventative Medicine (ATPM)/Centers for Disease Control
	Cooperative Agreement Subawards Program (\$758,000)
\item[2004-05] \emph{Regional Socieconomic Modeling in Support of Economic
  Development Networks.} Co-Principal Investigtor.\\ Sponsor: Defense Logistics
  Agency (\$987,000).
\item[2004-07] \emph{Editorial Office. International Regional Science Review}.
	Principal Investigator.\\
	Sponsor: SAGE Publications Incorporated. (\$60,000)
\item[2002] \emph{Identification of Industrial Clusters in Imperial County}.
	Principal Investigator. \\Sponsor: California Center for Border and
	Regional Economic Studies. (\$8,000).
\item[2001] \emph{Evaluation of Cluster Identification Methods at the Sub-State
	Scale}. Principal Investigator. \\Sponsor:  California Employment
	Development Department.  (\$30,000). 
\item[2001] \emph{Design of a Fiscal Impact Analysis Toolkit: FIAT. Principal
	Investigator}. \\Sponsor: SDSU Defense Conversion Center. (\$15,000). 
\item[2000] \emph{Open Source Approaches To Spatial Analysis}. Subcontract to Center
	for Spatially Integrated Social Sciences. (\$5,000). 
\item[2000] \emph{Analysis of the Visitor Industry Cluster in the San Diego
	Economy}. Principal Investigator. \\Sponsor: San Diego Workforce
	Partnership. (\$50,000).
\item[1999-03] \emph{Editorial Office. International Regional Science Review}.
	Principal Investigator.\\
	Sponsor: SAGE Publications Incorporated. (\$45,000)
\item[1999] \emph{Identifying Regional Industrial Clusters in the California
	Economy}. Principal Investigator. \\Sponsor: California Employment
	Development Department.  (\$20,000). 
\item[1998-99] \emph{Environmental Accounting for the San Diego-Tijuana
	Region}.
	Co-Principal Investigator.  \\Sponsor: Southwest Center on Environmental
	Research and Policy.  (\$49,000). 
\item[1998] \emph{Analysis of the Technician Needs Assessment Survey}.  Principal
	Investigator.  \\Sponsor: The San Diego Regional Economic Development
	Corporation (\$4,000). 
\item[1988] \emph{The East County Industry Connectory Project}, Consultant.  \\Sponsor:
	The East County Economic Development Corporation (\$2,000). 
\item[1997-98] \emph{The San Diego Economic Information and Modeling Project}.
	Co-Principal Investigator. \\Sponsor: Office of Economic Adjustment,
	U.S. Department of Defense (\$103,000). 
\item[1997] \emph{The Impact of International Trade on Sub-State Economies}.
	Principal Investigator. \\Sponsor: College of Arts and Letters
	Micro-Grants (\$332). 
\item[1997] \emph{Spatial Econometric Approaches to Simultaneous Equations
	Systems}.
	Principal Investigator.  \\Sponsor: Faculty Development Program, San
	Diego State University. Amount (\$4,000). 
\item[1996] \emph{The Impacts of the San Diego State University on the Regional
	Economy}. Co-Principal Investigator. \\Sponsor: Office of the Vice
	President for Academic Affairs, San Diego State University (\$20,000). 
\item[1995-96] \emph{The San Diego Economic Information and Modeling Project}.
	Co-Principal Investigator.  \\Sponsor: Office of Economic Adjustment,
	U.S. Department of Defense (\$243,000).
\item[1995] \emph{A Review of the San Diego Demographic and Economic Forecasting
	Model}. Consultant. \\Sponsor: The San Diego Association of Governments
	(\$4,200). 
\item[1994-95] \emph{The Economic Studies Project}.  Co-principal Investigator.
	\\Sponsor: Office of Economic Adjustment, U.S.  Department of Defense
	(\$241,592). 
\item[1993] \emph{Integration of Multiregional Modeling and Geographic Information
	Systems}. Principal Investigator.  \\Sponsor: Research, Scholarly and
	Creative Activity Awards, College of Arts and Letters, San Diego State
	University (\$3,885).  \end{cvlist}

\begin{cvlist}{Professional Associations}
\item Association of American Geographers\\ Regional Science
 Association International\\ 
 Western Regional Science Association \end{cvlist}

\begin{cvlist}{Courses Taught}
 \item[\textbf{Short and Invited Courses}]
 \item PySAL Workshop (RSAI 2014, Atlanta, GA)
 \item Exploratory spatial data analysis with PySAL (Yverdon-les-Bains, Switzerland)
 \item PySAL and GeoDaSpace (Ohio State University)
 \item Spatial Econometrics: Theory and Practice (Wageningen School of Social
   Sciences, Wageningen University).
 \item Introduction to Exploratory Spatial Data Analysis (West Virginia
   University)
 \item Python for Spatial Analysis (University of California, Santa Barbara)
 \item[\textbf{Arizona State University}]
\item Geographic Information Science I
\item Geographic Information Analysis
\item Geographics
\item Geocomputation
\item Open Source Tools for Planners
 \item[\textbf{San Diego State University}]
 \item Seminar in Geocomputation and Geovizualization (Co-taught with A.
     Skupin). 
 \item Open Source Geocomputation
 \item Seminar on Geographic Research Design
 \item Advanced Quantitative Methods in Geographic Research
 \item Regional and Urban Modeling
 \item Open Source Tools for Geographic Research
 \item Quantitative Methods in Geographic Research
 \item Location and Urban Spatial Structure
 \item Introduction to Geographic Information Systems
 \item Spatial Data Analysis
 \item Location of Economic Activities
 \item Introduction to Human Geography
\end{cvlist}

  \begin{cvlist}{Graduate Advising (* chair)}
 \item[\textbf{Post Doctoral Positions}]
  \item[2009] Myrna L. Sastr\'e Guti\'errez.* \emph{Regional Dynamics,
    Convergence, and Space in Mexico}
  \item[2005] Juan Carlos Duque.* \emph{Integrating Industrial and Spatial
    Clustering Methodolgies.}
  \item[2005] Oleg Smirnov.* \emph{Spatial Analytical Approaches Towards
    Economic Development}.
  \item[\textbf{Doctoral In Progress}]
  %\item[\textbf{Masters In Progress}]
 \item Jason Laura.* \emph{Towards a Taxonomy of Parallel Spatial
   Algorithms}. Arizona State University.
 \item Insu Hong. Arizona State University.
 \item Kevin Kane. Arizona State University.
 \item Joanna Merson. Arizona State University.

 \item[\textbf{Doctoral Completed}]

\item[2013] Boris Dev.* \emph{Assessing Inequality Using Geographic
  Income Distributions}. SDSU-UCSB Joint Doctoral Program.
\item[2013] Ran Wei. \emph{Addressing geographic Uncertainty in Spatial
  Optimization}. Arizona State University.
\item[2012] David Folch.* \emph{Residential Segregation Measures and their
  Spatial Properties.} Arizona State University.
\item[2012] Nicolas Malizia. Arizona State University.
\item[2012] Yin Liu. \emph{An exploratory toolkit for exploring
  rsidential movement patterns at a micro scale.}. Arizona State
  University.
\item[2011] Huaqun Li. \emph{Regional Inequality and Foreign Direct Investment in
  China}. George Mason University (Public Policy).
 \item[2010] Daniel Arribas-Bel. \emph{Essays on the Distribution and Spatial
   Structure of Cities}. Universidad de Zaragoza (Economics).
 \item[2010] Xinyue Ye.* \emph{Comparative Space-Time Dynamics}.
   SDSU-UCSB Joint Doctoral Program.
\item [2008] Myrna L. Sastr\'e Guti\'errez \emph{Multiregional Dynamic Modeling for
   a Transnational Region, Mexico-United States: A Space-Time Approach.}
   (Economics, Universidad Aut\'onoma De Baja California).
 \item[2007] Jared Aldstadt \emph{Analysis and Modeling of Dengue Virus Transmission
   in Space and Time.} SDSU-UCSB Joint Doctoral Program.
 \item[2006] Mark Janikas.* \emph{Regional Income Dynamcs: Clustering,
	 Scale, and Geocomputation}. SDSU-UCSB Joint Doctoral Program.
 \item[2003] Jennifer Miller. \emph{Incorporating Spatial Dependence into
	 Predictive Vegetation Maps.} SDSU-UCSB Joint Doctoral Program.
 \item[1999] Scott Munroe. \emph{The Economic and Spatial Dynamics of US
	 Metropolitan Retailing 1972-96.} SDSU-UCSB Joint Doctoral Program.
 \item[1999] Lauren Scott. \emph{The Accessible City: Employment Opportunities
	 in Time and Space.} SDSU-UCSB Joint Doctoral Program.
 \item[1998] Long Gen Ying. \emph{Modeling the Temporal and the Spatial
	 Dynamics of Chinese Economic Growth.} SDSU-UCSB Joint Doctoral Program.

 \item[\textbf{Masters Completed}]
 \item[2013] Sharisse Fisher. Arizona State University.
 \item[2012] Stephanie Kleinschmidt. Arizona State University.
 \item[2010] Martin Lacayo-Emery \emph{Self-organizing Map Toolkit}.
 \item[2008] Charles Schmidt.* \emph{Effects of Irregular Topology in Spherical
   Self-Organinzing Maps.}
\item[2008] Philip Stephens.* \emph{The Spatial Impact of Economic Development
   Policies: The Case of HUBZones in San Diego California}.
 \item[2008]   Esperb\'e, Aude. \emph{Towards High-Resolution Self-Organizing
   Maps of Geographic Features}. 
 \item[2007] Aarthi Ram. \emph{Spatial Algorithms in Python} (Computer Science).
 \item[2007] Xuening Li.* \emph{Max-p region based estimation of disease
   rates.}
 \item[2007] Maribel Elias.* \emph{Educational Convergence in Peru}.
 \item[2006] Valentine, Scott A. \emph{A Study of Hydrologic Response to the
   Restoration of Trout Creek, Central Sierra Nevada, California}.
 \item[2005] Funda Emine Sygin. \emph{Estimating the Demand for Air Quality in
   Southern California: A Hedonic Approach.} (Economics).
 \item[2005] Kristen Erickson. \emph{Defining Location, Location, Location in East
   San Diego  County: A Case of Spatial Non-stationarity?} 
\item[2004]   Michael Farrel \emph{Modeling Regimes in Watersheds}. 
\item[2004]   Elizabeth Reynolds \emph{Analysis of Woodpecker habitat}. (Biology). 
\item[2002]  Mark Janikas.* \emph{Integrating a Social Accounting Matrix into
	a Local Fiscal Impact Analysis Model}. 
\item[2001]  Daniel J. Mattheis.* \emph{The Spatial and Interindustry
	Characteristics of Industiral Clusters in the San Diego Region.}. 
\item[2001]  Deborah
Jones.* \emph{The Impact of Posted Beach Closures on Coastal Housing
Prices: A Spatial Hedonic Price Analysis}.
\item[2000] Maritzo Antonetti. \emph{Measuring the Performance of Urban
	Planning Through Urban Indicators: A Comparative Analysis of Quality
	of Life, Healthy Cities, and Urban Sustainability}.  (Public
	Administration and Urban Studies). 
\item[2000] Calvin McNeil. \emph{Crime and space in Los Angeles}.
	(Economics). 
\item[1999] Deana Simmons. \emph{Predicting the Effects of Environmental
	Variables Upon Potential Site Productivity of Chaparral in the
	Descanso Ranger District}. 
\item[1998]  Brett D.  Montouri.* \emph{Are US Regional Incomes Converging? A
	Spatial Analysis.}
\item[1998]  Boris Dev.* \emph{Integrating Spatial and Interindustry Structure
	in Dynamic Regional Econometric Models.}
\item[1988] Gregg Bohr. \emph{Cold Season Precipitation in the Rocky
	Mountains: Patterns of Accumulation and Variability.}
\item[1996] Frank.  P. Cuozzo. \emph{Mandibular Divergence in the Genus
	Tarsius: Its Relation to Basicranial Breadth.} (Anthropology). 
\item[1995] Bruce Frank. \emph{Developing a Fire Fuel Modification Plan at
	Camp Pendleton: Evaluating the Effectiveness of the Use of Preference
	Analysis Techniques in a Geographic Information System.}
\item[1994] Amy Bortman.  \emph{An Integrated Spatial Analysis/GIS Procedure
	for Estimating Suppressed County Employment Data.}
\item[1994] Caroline Sallaway.  \emph{Evaluation of the Effectiveness of
	Perceptually Ordered Color Schemes for Maps.}
\end{cvlist}

\begin{cvlist}{Service to University and Community}
\item[\textbf{Department/School}]
\item[2013] Chair, Director Search Committee 
\item[2011-] Chair, Computing Committee
\item[2010-11] Chair, Academic Program Review Committee
\item[2009-11] Member, Executive Committee
\item[2009-11] Chair, Personnel Committee
\item[2008-] Member, GeoDa Center Executive Committee
\item[2008-] Chair, Computing Committee
\item[2007] Chair
\item[2006] Chair, Computing Commitee\\
  	    Chair, Hiring Committee\\
	    Member, Ph.D. Committee
\item[2005] Chair, Computing Commitee\\
  	    Hiring Committee
\item[2004] Chair, Computing Committee\\
  Hiring Committee
\item[2003] Chair, Computing Committee
\item[2002] Chair, Internal Resource Committee
\item Member, Policy Advisory Committee
\item[2001] Chair, Internal Resources Committee
\item[2000] Chair, Internal Resources Committee
\item[2000] Member, Speakers and Community Relations Committee
\item[1999] Chair, Personnel Committee
\item Member, Policy Advisory Committee
\item Member, Ph.D. Committee
\item[1998] Member, Policy Advisory Committee
\item Member, MA Committee
\item Member, Personnel Committee
\item[1997] Member, MA Committee
\item Member Internal Resources Committee
\item[1996] Member, MA Committee
\item[1995] Member, Hiring Committee
\item[1994] Chair, Speakers and Public Relations Committee

\item[\textbf{College}]
\item[2009-] Member, Academic Standards Committee
\item[2004] Member, Tenure and Promotion Committee
\item[2003] Member, Tenure and Promotion Committee
\item[1999] Member, Academic Planning Committee
\item[1998] Member, Academic Planning Committee
\item[1994] Coordinator, California State University Student Research Conference

\item[\textbf{University}]
\item[2006-08] Member, General Education Task Force
\item[2005] Member, Tenure and Promotion Committee, Library
\item[2003] Academic Senate
\item[2003] College of Arts and Letters Dean Search Committee
\item[1998] Technical Advisor, Region Wide Economic Impacts of
  Higher Education.
\item[1996] Co-Principal Investigator: SDSU Economic Impact Report.

\item[\textbf{Community}]
\item[1998] Technical Advisory Panel. Series 9 Demographic and
  Economic Forecasts. San Diego Association of Governments.
\item[1998] Technical Advisory Panel. Evaluating Regional
  Prosperity. San Diego Association of Governments.

\item[\textbf{Profession}]
 \item[2013--] Organizing Committee, Scientific Computing with Python (SciPy)
   Meeting
 \item[2013--] Scientific Committee, Open Source Geospatial Research and
   Education Meeting.
 \item[2012--] Methodology, Measurement, and Statistics Panel Member. National
   Science Foundation
 \item[2010--] External Advisory Board Member, Regional Research Institute,
   West Virginia University
 \item[2009] Program Chair, North American Meetings of the Regional Science
   Association.
 \item[2009-10] Geography and Spatial Sciences Senior Panel Member. National Science
   Foundation.
 \item[2005] Scientific Committee. Workshop on Spatial Econometrics. Kiel
   Institute for World Economics.
 \item[2005-09] Councillor, North American Regional Science Assocation.
 \item[2005--] Board of Directors, Western Regional Science Association.
 \item[2005] Judge, William H. Miernyk Research Excellence  Medal.
   Southern Regional Science Association.  
\item[2001] Judge, Regional Science Association International Dissertation
  Competition.
\item[1996--] Proposal reviewer, \emph{National Science Foundation}
 \item[Journal Referee (not including editorial appointments)] \item
  \emph{Annals of Regional Science\\ Economic Systems Research\\Environment and Planning A\\
  European Economic Review\\ Geographical Analysis\\Geographical Systems\\
  Growth and Change\\ International Journal of Geographic Information
  Systems\\International Regional Science Review \\Journal of
  Applied Econometrics\\Journal of Economic Geography\\ Journal of Regional
  Science\\ Papers in Regional Science\\The Professional Geographer\\ Regional
  Science and Urban Economics\\Regional Studies\\Review of Regional Studies}
  \end{cvlist}

\end{cv}
\end{document}
\endinput 
